---
title: "Asthma-Mali Output"
author: "Rachel Laufer"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(knitr)
source("asthma_calcs_point_estimates.R")
```

## RSV-LRTI cases through first 3 years

RSV-LRTI cases for no intervention (status quo)
```{r LRTI_no}
kable(CI_LRTI_age_no)
```

RSV-LRTI cases for llAb
```{r LRTI_llAb}
kable(CI_LRTI_age_llAb)
```

RSV-LRTI cases for llAb + pVax
```{r LRTI_llAb_pVax}
kable(CI_LRTI_age_llAb_pVax)
```

### RSV-LRTI percent decrease compared to status quo through first 3 years

percent decrease for llAb
```{r LRTI_pd_llAb}
kable(CI_LRTI_pd_llAb)
```

percent decrease for llAb + pVax
```{r LRTI_pd_llAb_pVax}
kable(CI_LRTI_pd_llAb_pVax)
```

## RSV-LRTI hospitalizations through first 3 years

RSV-LRTI hospitalizations for no intervention (status quo)
```{r hosps_no}
kable(CI_hosps_age_no)
```

RSV-LRTI hospitalizations for llAb
```{r hosps_llAb}
kable(CI_hosps_age_llAb)
```

RSV-LRTI hospitalizations for llAb + pVax
```{r hosps_llAb_pVax}
kable(CI_hosps_age_llAb_pVax)
```
### RSV-LRTI hospitalizations percent decrease compared to status quo through first 3 years

percent decrease for llAb
```{r hosps_pd_llAb}
kable(CI_hosps_pd_llAb)
```

percent decrease for llAb + pVax
```{r hosps_pd_llAb_pVax}
kable(CI_hosps_pd_llAb_pVax)
```

## RSV-LRTI deaths through first 3 years

RSV-LRTI deaths for no intervention (status quo)
```{r deaths_no}
kable(CI_deaths_age_no)
```

RSV-LRTI deaths for llAb
```{r deaths_llAb}
kable(CI_deaths_age_llAb)
```

RSV-LRTI deaths for llAb + pVax
```{r deaths_llAb_pVax}
kable(CI_deaths_age_llAb_pVax)
```

### RSV-LRTI deaths percent decrease compared to status quo through first 3 years

percent decrease for llAb
```{r deaths_pd_llAb}
kable(CI_deaths_pd_llAb)
```

percent decrease for llAb + pVax
```{r deaths_pd_llAb_pVax}
kable(CI_deaths_pd_llAb_pVax)
```

## RSV-attributable and total recurrent wheeze or asthma prevalence at 6 years of age by intervention

RSV-LRTI attributable wheeze/asthma at 6 years
```{r att_asth}
kable(CI_att_df)
```

RSV-LRTI attributable wheeze/asthma per 10,000 children at 6 years
```{r att_asth_pr}
kable(CI_att_pr_df)
```

RSV-LRTI attributable wheeze/asthma at 6 years, percent decrease from status quo
```{r att_asth_pd}
kable(CI_att_pd_df)
```

Total recurrent wheeze/asthma
```{r tot_asth}
kable(CI_tot_asth_df)
```

Total recurrent wheeze/asthma per 10,000 children at 6 years
```{r tot_asth_pr}
kable(CI_tot_asth_pr_df)
```

Total recurrent wheeze/asthma, percent decrease from status quo
```{r tot_asth_pd}
kable(CI_tot_asth_pd_df)
```

Total recurrent wheeze/asthma "All RSV-LRTI prevented"
```{r all_rsv}
kable(CI_all_rsv_df)
```